data_collation

### 2024-05-23 scripts/data_collation.Rmd
added rugosity dataframe clean

# use rbind.fill() method in R to combine data frames with different columns
swath_data <- rbind.fill(swath_2018, Swath_count, FtWeatherill_Swath_2016_wide)

@@

>>>>

# rename swatch category columns in kelp_swath 2023 and kelp swath 2022
kelp_swath_2022 <- kelp_swath_2022 %>%
  rename(
    "0-20 IN" = "X0.20.IN",
    "20-40 IN" = "X20.40.IN",
    "40-20 OFF" = "X40.20.OFF",
    "20-0 OFF" = "X20.0.OFF"
  )

# remove columns with observer and unneeded data
kelp_swath_2022 <- kelp_swath_2022[ -c(15:22) ]

# rename KB to King's Beach and FW to Fort Wetherill
kelp_swath_2022$SITE[kelp_swath_2022$SITE == "FW"] <- "Fort Wetherill"
kelp_swath_2022$SITE[kelp_swath_2022$SITE == "KB"] <- "King's Beach"

# rename swatch category columns in kelp_swath 2023 and kelp swath 2022
kelp_swath_2023 <- kelp_swath_2023 %>%
  rename(
    "0-20 IN" = "X0.20.IN",
    "20-40 IN" = "X20.40.IN",
    "40-20 OFF" = "X40.20.OFF",
    "20-0 OFF" = "X20.0.OFF"
  )

# remove columns with observer and unneeded data
kelp_swath_2023 <- kelp_swath_2023[ -c(12) ]

# rename KB to King's Beach and FW to Fort Wetherill
kelp_swath_2023$SITE[kelp_swath_2023$SITE == "FW"] <- "Fort Wetherill"
kelp_swath_2023$SITE[kelp_swath_2023$SITE == "KB"] <- "King's Beach"

# rename swatch category columns in 2019, 2020, and 2021 swath
swath_2021 <- swath_2021_DEM %>%
  rename(
    "0-20 IN" = "X0.20.IN",
    "20-40 IN" = "X20.40.IN",
    "40-20 OFF" = "X40.20.OFF",
    "20-0 OFF" = "X20.0.OFF"
  )

# rename KB to King's Beach and FW to Fort Wetherill
swath_2021$SITE[swath_2021$SITE == "Fort Weatherill"] <- "Fort Wetherill"
swath_2021$SITE[swath_2021$SITE == "Kings Beach"] <- "King's Beach"

# rename swatch category columns in 2019, 2020, and 2021 swath
swath_2020 <- swath_2020_DEM %>%
  rename(
    "0-20 IN" = "X0.20.IN",
    "20-40 IN" = "X20.40.IN",
    "40-20 OFF" = "X40.20.OFF",
    "20-0 OFF" = "X20.0.OFF"
  )

# rename Fort weatherill to Fort Wetherill
swath_2020$SITE[swath_2020$SITE == "Fort Weatherill"] <- "Fort Wetherill"

# rename swatch category columns in 2019, 2020, and 2021 swath
swath_2019 <- swath_2019_DEM %>%
  rename(
    "0-20 IN" = "X0.20.IN",
    "20-40 IN" = "X20.40.IN",
    "40-20 OFF" = "X40.20.OFF",
    "20-0 OFF" = "X20.0.OFF"
  )

# use rbind.fill() method in R to combine data frames with different columns
swath_data <- rbind.fill(swath_2018, swath_2019, swath_2020, swath_2021, Swath_count, FtWeatherill_Swath_2016_wide, kelp_swath_2022, kelp_swath_2023)

@@

# Combine rugosity dataframes
```{r}
